Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-01 outputs/paper/paper.Rmd
ggplot

```{r}
data %>%
  ggplot(aes(x = Variable, y = Health_Record)) +
  geom_bar(stat='identity') +
  coord_flip()
```

Talk more about it.

>>>>

```{r}
ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
```
```{r}
ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
```
```{r}
ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
```
```{r}
ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
```
Talk more about it.
